---
title: 'Homework 2'
author: "Zach Josten"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/9/2022 before 11:59pm. Submit in Canvas (file upload).  

1.\
Zach Josten - <https://github.com/ZachJosten/Homework2-ZJ>\
\
Craig Orman - <>\
\
Number of pull requests made - \
Requests made to - <>\
\
Number of pull requests accepted - \
Requests accepted from - <>\
\
Tips for Git/Github  
1. If working on a fork, make sure to fetch upstream before you start working on the fork in case changes were made.  
2. Adding comments on a commit or pull request can help when trying to keep track of changes made.  
3. It is important to pull from the repository before working on something.  


    


2. 
```{r}
library(ggplot2)
t = read.csv("gapminder-5060.csv")
usGap = subset(t, country == "United States")
canGap = subset(t, country == "Canada")
finGap = rbind(usGap, canGap)
ggplot(data = finGap, aes(y = lifeExp, x = gdpPercap, group = country, color = country)) + geom_line()
```

3.\
In my opinion images like [this](https://external-content.duckduckgo.com/iu/?u=https%3A%2F%2Fvrzkj25a871bpq7t1ugcgmn9-wpengine.netdna-ssl.com%2Fwp-content%2Fuploads%2F2018%2F08%2Fvisualization-of-example-linear-regression-in-r.png&f=1&nofb=1) are what I consider data science(image courtesy of r-crafts.org). Data science plays around the ideas of\
1. Compilation of data\
2. Analysis of data\
3. Modeling of data\
4. Prediction using models\
5. Testing models\
In current age data can play a big role in our lives especially with the internet at our fingertips. Data science is such a pivotal field in the progression of humanity. The image provided shows a linear regression model, which was built from first compiling a bunch of data, then filtering, training and polishing a model. While this may sound like a bunch of nonsense to an average person, it may fit into the daily life of an average person, things such as GPS, weather reports, baseball statistics, stock markets, etc. All of these things can have innumerable amounts of data, something which data science can turn into a simpler to understand and usable piece of information. I think that the image I chose is a simple but practical example of what data science is capable of, compiling data into workable tools to improve the every day lives of humanity. 



